Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
minor edit

Then, we compare the approximation made by computing curvature from level $l >
l_0$ in order to accelerate visualisation with the ground truth result obtained
at level $l_0$. We also compare them with the hierarchical algorithm discussed
in Section~\ref{sec:hierarchical}. The results are presented in
Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.

We can first see that the number of texel fetch required to compute
the curvature reduces drastically when computing the approximations.
This is mandatory if we want to increase the framerate.
However, we can also note that the error increases quite slowly.
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to
the $l_0$ level.
Thanks to this low error, higher approximation levels are visually
very similar to the $l_0$ level. We can therefore use them for exploring our
datasets in real time, changing the radii on the fly and visualising dynamic datasets.

@@

	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}

	\begin{tabular}{@{}lrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=16$}\\
      \cmidrule(r){2-7}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      5706 & 2 & 28 & 90 & 2120 & 17080\\
      %Time (in ms) &
      %826 & 14 & 26 & 252 & 606 & 4801\\
      $L_\infty$ error (\wrt $l_0$) &
      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
      $L_2$ error (\wrt $l_0$) &
      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}

  \end{center}
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
  The object was triangulated at full resolution with a regular grid and contains 282,396 vertices. The timings
    only consider the curvature estimation step.\label{tab:full-res-stat}}
\end{table}

>>>>

Then, we compare the approximation made by computing curvature from level $l >=
l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
seems to fastly converge to the ground truth results.
Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (worst
case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
fetches. We can first see that the number of texel fetch required to compute the
curvature reduces drastically when computing the approximations. This is
mandatory if we want to increase the framerate.

 in order to accelerate visualisation with the ground truth result obtained
at level $l_0$. We also compare them with the hierarchical algorithm discussed
in Section~\ref{sec:hierarchical}. The results are presented in
Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.

However, we can also note that the error increases quite slowly.
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to
the $l_0$ level.
Thanks to this low error, higher approximation levels are visually
very similar to the $l_0$ level. We can therefore use them for exploring our
datasets in real time, changing the radii on the fly and visualising dynamic datasets.

@@

	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}
	\begin{tabular}{@{}lrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=16$}\\
      \cmidrule(r){2-7}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      5706 & 2 & 28 & 90 & 2120 & 17080\\
      %Time (in ms) &
      %826 & 14 & 26 & 252 & 606 & 4801\\
      $L_\infty$ error (\wrt $l_0$) &
      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
      $L_2$ error (\wrt $l_0$) &
      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}
  \end{center}
  %
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error
  obtained on OctaFlower with a digital domain of $130^3$ when computing mean
  curvature, with two radii: 8 and 16. The object is triangulated at full
  resolution with a regular grid and contains 282,396 vertices.
  %
  \label{tab:full-res-stat}}
  %
\end{table}
